Artin Group Presentations Arising from Cluster Algebras

### 2014-07-22 Paper.tex
More Section 5 Changes
improved section 6

\begin{lem}\label{lem:chordless_cycles}
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices. Every chordless cycle in $\Gamma'$ is of one of these types.

@@

\begin{lem}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

@@

As a result of these lemmas, we immediately obtain the following corollary:

\begin{cor}
Let $\Gamma$ be a diagram of finite type. Then the group A($\Gamma$) defined in the introduction is isomorphic to the group A$_{\Gamma}$
\end{cor}

@@

\begin{lem}\label{lem:op_homomorphism}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$. To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$. But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$

@@

\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have that \todo{refer to lemma}
\begin{align*}
s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
&= e
\end{align*}

@@

\begin{proof}
We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.  By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.

\begin{enumerate}[a)]
\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_k^{-1}t_it_kt_j$

\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$

\item We have $ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$

\item We have that
\begin{align*}
t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
&= e\\
\end{align*}

\item
Without loss of generality we label the vertices as follows:\todo{insert diagrams}

\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\item
\begin{align*}
t_4^{-1}t_1^{-1}t_2^{-1}t_3t_2t_1 &= s_4\underline{s_1^{-1}s_1}s_2^{-1}\underline{s_1^{-1}s_3s_1}s_2 \underline{s_1^{-1}s_1}\\
&= s_4s_2^{-1}s_3s_2\\
&= s_2^{-1}s_3s_2s_4\\
&= (s_1^{-1}s_1)s_2^{-1}(s_1^{-1}\underline{s_1)s_3(s_1^{-1}}s_1)s_2(s_1^{-1}s_1s_4\\
&= s_1^{-1}1s_2^{-1}s_1^{-1}s_3s_1s_2s_1^{-1}s_1s_4\\
&= t_1^{-1}t_1^{-1}t_3t_2t_1t_4\\
\end{align*}

\item
\begin{align*}
t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4 &= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
&= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
&= s_1s_1^{-1}\\
&= e\\
\end{align*}

\item
\begin{align*}
t_2t_3^{-1}t_4t_3 &= s_2s_3^{-1}\underline{s_1s_4s_1^{-1}}s_3\\
&= s_2s_3^{-1}s_4^{-1}s_1s_4s_3\\
&= s_3^{-1}\underline{s_4^{-1}s_1s_4}s_3s_2\\
&= s_3^{-1}s_1s_4s_1^{-1}s_3s_2\\
&= t_3^{-1}t_4t_3t_2\\
\end{align*}

\item
\begin{align*}
& t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= e\\
\end{align*}

\item
\begin{align*}
& t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
&= e\\
\end{align*}
\end{enumerate}
\end{proof}

>>>>

\todo[inline]{directions of arrows within squares?}
\begin{lem}\label{lem:chordless_cycles}
Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle. Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices. Every chordless cycle in $\Gamma'$ is of one of these types.

@@

\begin{lem}\label{lem:extra_square_relation}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

@@

@@

\begin{lem}\label{lem:op_homomorphism}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$. In particular, A$_{\Gamma}$ $\cong$ A$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$. To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$. But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$

@@

\end{enumerate}
\item
\begin{enumerate}[i)]
\item We have that
\begin{align*}
s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
&= e
\end{align*}

Where the second equality follows from Lemma \ref{lem:extra_square_relation}.

@@

\begin{proof}
We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that a cycle relation holds in each case.  We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.

\begin{enumerate}[a)]
\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$

\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_3t_1$

\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$

\item We have
\begin{align*}
t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1 &= s_2s_3s_2^{-1}s_1^{-1}s_2s_1s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
&= s_2s_3s_1s_2s_1^{-1}s_2^{-1}s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2^{-1}\\
&= s_2s_1s_2s_1^{-1}s_3s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2\\
&= e\\
\end{align*}

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
&= s_1s_3^{-1}s_4s_3\\
&= s_3^{-1}s_4s_3s_1\\
&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
&= s_2^{-1}2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\item We have
\begin{align*}
t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4 &= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
&= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
&= s_1s_1^{-1}\\
&= e\\
\end{align*}

\item We have
\begin{align*}
t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3\\
&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
&= t_4^{-1}t_1t_4t_3\\
\end{align*}

\item We have
\begin{align*}
& t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= e\\
\end{align*}

\item We have
\begin{align*}
& t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
&= e\\
\end{align*}
\end{enumerate}
\end{proof}
